Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-01 paper/tex/sections/introduction.tex
we detected a BHNS!!

One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS). Of all the events detected by ground-based detectors, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}. Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars. These binaries are expected to have electromagnetic counterparts that can studied in the same way as NSNSs. A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}. These systems could be observed not only by gravitational wave detectors, but also radio telescopes such as MeerKAT and SKA, which will help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.

>>>>

One particularly interesting potential LISA source is a black hole neutron star binary (BHNS). With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}. However, with only two detections (not including the low-confidence candidates GW190425 and GW190184 \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain. Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars. These binaries are expected to have electromagnetic counterparts that can studied in the same way as NSNSs. A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}. These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and SKA, which will help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.

### 2021-07-01 paper/tex/sections/methods.tex
we detected a BHNS!!

\subsection{Gravitational wave detection}\label{sec:gw_detection}
We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to evolve binaries and calculate their LISA detectability. For a full derivation of the equations given below please see the LEGWORK release paper (Wagg et al. in prep) or the \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{documentation}.

>>>>

\subsection{Gravitational wave detection}\label{sec:gw_detection}
We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to evolve binaries and calculate their LISA detectability. For a full derivation of the equations given below please see the LEGWORK release paper, Wagg et al. 2021b (in prep), or the \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{documentation}.

### 2021-07-01 paper/tex/sections/results.tex
fix file paths
we detected a BHNS!!

In this section we present our main results for the detectable LISA DCO population. We find that on average, for our fiducial model, a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (c.f.\ Table~\ref{tab:detection_rates}). We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.

@@

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}. \todo{subject to change with the updated/new models and new uncertainty estimates}}
    \label{fig:detection_rates}
\end{figure*}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/chirp_mass_uncertainty_4yr.pdf}
    \caption{Cumulative distribution function for error on the chirp mass. Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). Shaded region indicates region with unmeasureable chirp mass.}
    \label{fig:m_c_unc}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/angular_resolution_4yr.pdf}
    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}
    \label{fig:ang_res}
\end{figure}

>>>>

In this section we present our main results for the detectable LISA DCO population. We find that on average, for our fiducial model, a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (c.f.\ Table~\ref{tab:detection_rates}). We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and the parameter distributions for detectable sources in Section~\ref{sec:fiducial_distributions}.

@@

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}. See Sec.~\ref{sec:detection_rate_analysis} for a discussion. \todo{subject to change with the updated/new models and new uncertainty estimates}}
    \label{fig:detection_rates}
\end{figure*}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{chirp_mass_uncertainty_4yr.pdf}
    \caption{Cumulative distribution function for error on the chirp mass. Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping). Shaded region indicates region with unmeasureable chirp mass.}
    \label{fig:m_c_unc}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{angular_resolution_4yr.pdf}
    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}
    \label{fig:ang_res}
\end{figure}
